CRUSE to Safe Cycling in Ireland

### 2023-09-29 paper.qmd
Add bit to discussion, finish additions

However, travel to school and work only constitute a small proportion of all trips.
To overcome this issue, we developed a spatial interaction modelling methodology to estimate the number of trips between each OD pair for additional trip purposes.
The classification of trip purposes used in the CRUSE Tool was guided mainly by the trip purpose classification found within the National Household Travel Survey (NHTS), but with the addition of categories based on the comprehensive POWSCAR data, and the need to include recreational trips and multi-stage trips (not yet implemented).
An overview of the trip purposes used in CRUSE is presented in @fig-trip-purposes.

@@

The main result of the CRUSE project is an open access web application and datasets on current and potential future cycling levels in Ireland, with evidence provided at county and route segment levels.
Like the PCT on which CRUSE builds, a key feature of the results is that they are systematic and available for all counties, and most routes on which cycling is permitted, in Ireland.
The full set of results are therefore too extensive to present in their entirety in this paper.
Through the interactive web application, users can explore the data to generate the results that are most relevant to their needs, whether that is finding the cycling potential on a particular road or finding 'weak links' in the cycle network associated with a particular school, work place or other destination.

@@

The CRUSE Tool can help both in terms of describing the current situation, and also prioritise investment in those direct routes with high cycling potential that lack adequate cycling infrastructure, highlighted by @caulfield2012.

>>>>

However, travel to school and work only constitute around only 30% of all trips in Ireland.
To overcome this issue, we developed a spatial interaction modelling methodology to estimate the number of trips between each OD pair for additional trip purposes.
The classification of trip purposes used in the CRUSE Tool was guided mainly by the trip purpose classification found within the National Household Travel Survey (NHTS), but with the addition of categories based on the comprehensive POWSCAR data, and the need to include recreational trips and multi-stage trips (not yet implemented).
An overview of the trip purposes used in CRUSE is presented in @fig-trip-purposes.

@@

The main result of the CRUSE project is an open access web application and datasets on current and potential future cycling levels in Ireland, with evidence provided at county and route segment levels.
Like the PCT on which CRUSE builds, a key feature of the results is that they are systematic and available for all counties, and most routes on which cycling is permitted, in Ireland.
The full set of results are therefore too extensive to present in their entirety in this paper.
Through the interactive web application, users can explore the data to generate the results that are most relevant to their needs, whether that is finding the cycling potential on a particular road or finding 'weak links' or barriers in the cycle network associated with a particular school, work place or other destination.

@@

The CRUSE Tool can help both in terms of describing the current situation, and also prioritise investment in those direct routes with high cycling potential that lack adequate cycling infrastructure, highlighted by @caulfield2012.
It will also support reporting for the RISM Directive on road casualties as part of the road safety management system.

While the CRUSE Tool is not the first national and publicly available tool for cycling planning, it has some unique features that make it relevant for other countries, and other national road authorities tasked with making their transport systems safe.

TODO: outline these features.

The CRUSE Tool is designed to be used by a wide range of stakeholders, including transport planners, engineers, and other professionals, as well as non-professionals.
